### 2020-08-24 tex/article/cover.Rmd

---
title: "Utilizando a Regressão Logística para Classificação de Churn em um Ambiente de Startup"
author: "Antonio C. da Silva Júnior"
orientador: "Prof. WALMES M. ZEVIANI"
output:
  pdf_document:
    template: Capa.tex
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```